High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-04-04 notebooks/synthetic.qmd
uh

# Classifiers:
epochs = 100
link_fun = sigmoid
logreg = NeuralNetworkClassifier(builder=MLJFlux.Linear(σ=link_fun), epochs=epochs)
mlp = NeuralNetworkClassifier(builder=MLJFlux.MLP(hidden=(32,), σ=link_fun), epochs=epochs)
ensmbl = EnsembleModel(model=mlp, n=5)
classifiers = Dict(
    :logreg => logreg,
    :mlp => mlp,
    # :ensmbl => ensmbl,
)

@@

            # CCE for given classifier, coverage, temperature and λ:
            generator = CCEGenerator(temp=temp, λ=λ)
            @assert predict_label(M, data, x) != target_label
            ce = try
                generate_counterfactual(
                    x, target_label, data, M, generator;
                    initialization=:identity,
                )
            catch
                missing
            end

>>>>

# Classifiers:
epochs = 100
link_fun = sigmoid
logreg = NeuralNetworkClassifier(builder=MLJFlux.Linear(σ=link_fun), epochs=epochs)
mlp = NeuralNetworkClassifier(builder=MLJFlux.MLP(hidden=(32,), σ=link_fun), epochs=epochs)
ensmbl = EnsembleModel(model=mlp, n=5)
classifiers = Dict(
    # :logreg => logreg,
    :mlp => mlp,
    # :ensmbl => ensmbl,
)

@@

            # CCE for given classifier, coverage, temperature and λ:
            generator = CCEGenerator(temp=temp, λ=λ)
            @assert predict_label(M, data, x) != target_label
            ce = try
                generate_counterfactual(
                    x, target_label, data, M, generator;
                    initialization=:identity,
                    converge_when=:generator_conditions,
                )
            catch
                missing
            end
